Second-Generation Web Interface to Correcting ASR Output

### 2018-04-05 2018-ftc-vancouver/webapp-anon.tex
correct case for title

\begin{document}
\mainmatter              % start of a contribution
%
\title{Second-Generation Web Interface to Correcting ASR output}
%
\titlerunning{Second-Generation Web Interface to Correcting ASR output}  % abbreviated title (for running head)
%                                     also used for the TOC unless
%                                     \toctitle is used
%
\author{John Doe and Joan Doe}
%
\authorrunning{John Doe and Joan Doe} % abbreviated author list (for running head)
%
%%%% list of authors for the TOC (use if author list has to be modified)
%\tocauthor{Ivar Ekeland, Roger Temam, Jeffrey Dean, David Grove,
%Craig Chambers, Kim B. Bruce, and Elisa Bertino}
%
\institute{Unnamed University\\
           Faculty of Placeholder Arts\\
           Example Institute\\
           Street 42, City, Country\\
           \{john.doe,joan.doe\}@example.com}

>>>>

\begin{document}
\mainmatter              % start of a contribution
%
\title{Second-Generation Web Interface to Correcting ASR Output}
%
\titlerunning{Second-Generation Web Interface to Correcting ASR Output}  % abbreviated title (for running head)
%                                     also used for the TOC unless
%                                     \toctitle is used
%
\author{John Doe and Joan Doe}
%
\authorrunning{John Doe and Joan Doe} % abbreviated author list (for running head)
%
%%%% list of authors for the TOC (use if author list has to be modified)
%\tocauthor{Ivar Ekeland, Roger Temam, Jeffrey Dean, David Grove,
%Craig Chambers, Kim B. Bruce, and Elisa Bertino}
%
\institute{Unnamed University\\
           Faculty of Placeholder Arts\\
           Example Institute\\
           Street 42, City, Country\\
           \{john.doe,joan.doe\}@example.com}

### 2018-04-05 2018-ftc-vancouver/webapp.tex
correct case for title

\begin{document}
\mainmatter              % start of a contribution
%
\title{Second-Generation Web Interface to Correcting ASR output}
%
\titlerunning{Second-Generation Web Interface to Correcting ASR output}  % abbreviated title (for running head)
%                                     also used for the TOC unless
%                                     \toctitle is used
%
\author{Old\v{r}ich Kr\r{u}za and Vladislav Kubo\v{n}}
%
\authorrunning{Kr\r{u}za, Kubo\v{n}} % abbreviated author list (for running head)
%
%%%% list of authors for the TOC (use if author list has to be modified)
%\tocauthor{Ivar Ekeland, Roger Temam, Jeffrey Dean, David Grove,
%Craig Chambers, Kim B. Bruce, and Elisa Bertino}
%
\institute{Charles University\\
           Faculty of Mathematics and Physics\\
           Institute of Formal and Applied Linguistics\\
           Malostransk\'{e} n\'{a}m. 25, Prague, Czech Republic\\
           \{kruza,vk\}@ufal.mff.cuni.cz}

>>>>

\begin{document}
\mainmatter              % start of a contribution
%
\title{Second-Generation Web Interface to Correcting ASR Output}
%
\titlerunning{Second-Generation Web Interface to Correcting ASR Output}  % abbreviated title (for running head)
%                                     also used for the TOC unless
%                                     \toctitle is used
%
\author{Old\v{r}ich Kr\r{u}za and Vladislav Kubo\v{n}}
%
\authorrunning{Kr\r{u}za, Kubo\v{n}} % abbreviated author list (for running head)
%
%%%% list of authors for the TOC (use if author list has to be modified)
%\tocauthor{Ivar Ekeland, Roger Temam, Jeffrey Dean, David Grove,
%Craig Chambers, Kim B. Bruce, and Elisa Bertino}
%
\institute{Charles University\\
           Faculty of Mathematics and Physics\\
           Institute of Formal and Applied Linguistics\\
           Malostransk\'{e} n\'{a}m. 25, Prague, Czech Republic\\
           \{kruza,vk\}@ufal.mff.cuni.cz}
